---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mutalisk

<!-- badges: start -->
[![R-CMD-check](https://github.com/selkamand/mutalisk/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/selkamand/mutalisk/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/selkamand/mutalisk/branch/main/graph/badge.svg)](https://app.codecov.io/gh/selkamand/mutalisk?branch=main)
[![CRAN status](https://www.r-pkg.org/badges/version/mutalisk)](https://CRAN.R-project.org/package=mutalisk)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

mutalisk is an R package that produces cohort-level visualisations from the files output by [**mutalisk**](http://mutalisk.org/).

Note [CRUX](https://ccicb.shinyapps.io/crux/) is a GUI tool that makes it easy to export data in mutalisk compatible formats, and also provides a GUI interface to this package in the 'Mutational Signatures' module.
For a no-code solution, consider using the web app.

## Installation

You can install the development version of mutalisk from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("selkamand/mutalisk")
```

## Usage

First you have to generate mutalisk file: 

1. Start by following the instructions on the [**mutalisk**](http://mutalisk.org/) website

2. Once the results are ready, Select `Mutational Signature (Best only)`

3. Then click `Get the selected result for all samples at once`

4. Unzip the file

5. Parse the directory with `mutalisk_best_signature_directory_to_dataframe` and plot with `plot_stacked_bar`


```{r example}
library(mutaliskRutils)

# Read files in mutalisk_dir into 
mutalisk_dir <- system.file("lusc_tcga", package = "mutaliskRutils")
mutalisk_df <- mutalisk_best_signature_directory_to_dataframe(mutalisk_dir)

# Plot Cohort Data
plot_stacked_bar(mutalisk_df)
```
